Verification of the CVM algorithm with a new Recursive Analysis Technique

### 2025-01-23 isabelle/CVM_Subsample/document/root.tex
Document preparation: More minor refinements.

\documentclass[11pt,a4paper]{article}
\usepackage{isabelle,isabellesym}
\usepackage{amsfonts,amsmath, amssymb}

@@

\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

@@

\begin{abstract}
In 2022, Chakraborty et al.~\cite{chakraborty22} published a streaming algorithm for the distinct
elements problem, that deviated considerably from the state-of-the art, both due to its simplicity
and avoidance of standard derandomization techniques, while still maintaining a close to optimal
logarithmic space complexity.

>>>>

\documentclass[11pt,a4paper]{article}
\usepackage{isabelle,isabellesym}
\usepackage{amsfonts,amsmath, amssymb}
\usepackage[top=1.4in, bottom=1.4in, left=1.4in, right=1.4in]{geometry}

@@

\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}
\let\oldsection\section
\renewcommand\section{\clearpage\oldsection}

@@

\begin{abstract}
In 2022, Chakraborty et al.~\cite{chakraborty2022} published a streaming algorithm for the distinct
elements problem, that deviated considerably from the state-of-the art, both due to its simplicity
and avoidance of standard derandomization techniques, while still maintaining a close to optimal
logarithmic space complexity.
